Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-13 notes.tex
obtained relations between dimer and parent Hubbard parameters; the scaling with N is such that both the parent and the renormalized hubbard parameters scale similarly with N$

\title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
\author{}%Abhirup Mukherjee, Dr. Siddhartha Lal}
\begin{document}
\maketitle
\section{Introduction}
This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach. The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath. The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$. The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
\begin{align}
H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
\end{align}
Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice. It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system. The difference, however, lies in the following points:
\begin{itemize}
	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians. The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal. This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance. The present method, however, brings about the translational invariance in a different way. It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
\end{itemize}
The meaning of each of these statements will become clearer when we describe the method in more detail.

@@

@@

\item[1.] Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism. Compare with what is obtained from DMFT and its improvements. Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
\item[2.] While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well. We will provide these expressions at a later point in time. 
\item[3.] Study various other models of strong correlation with this approach:~(i) 

>>>>

\title{Generating Hubbard Model Solutions from Anderson Impurity Model Solutions}
\author{Abhirup Mukherjee, Dr. Siddhartha Lal}
\begin{document}
\maketitle
\section{Introduction}
This is an attempt to obtain various quantities like Greens functions, self-energies, spectral functions and (if possible) energies and wavefunctions of the Hubbard model, using a cluster-bath approach. The cluster-bath system is taken to be a single-impurity Anderson model with a correlated bath. The correlation will be brought about in two ways: a self-energy $\Sigma(k,\omega)$ of the bath, and a double occupancy repulsion cost $U_b$. The Hubbard and the correlated single-impurity Anderson models are defined using the Hamiltonians
\begin{align}
H_\text{hubb} &= -t^H\sum_{\sigma,\left<i,j \right>}\left(c^\dagger_{i\sigma} c_{j\sigma} + \text{h.c.}\right) + U^H\sum_i \hat n_{i \uparrow} \hat n_{i \downarrow} - \mu^H \sum_{i\sigma}\hat n_{i\sigma}\\
H_\text{siam} &= \sum_{k\sigma}\left[\epsilon_k + \Sigma(k,\omega)\right]\hat n_{k\sigma} + \epsilon_d^A \sum_\sigma\hat n_{d\sigma} + U^A \hat n_{d \uparrow} \hat n_{d \downarrow} + U_b \sum_{kk^\prime}\hat n_k \hat n_{k^\prime} -t^A\sum_{k\sigma}\left(c^\dagger_{d\sigma}c_{k\sigma} + \text{h.c.}\right) \label{clus_bath_siam}
\end{align}
Broadly speaking, the method involves first solving the SIAM using a unitary renormalisation group approach, to get the low energy effective theory, and then combining the low energy Hamiltonians in a symmetrized fashion to get the Hamiltonian for the Hubbard model lattice. It is reminescent of dynamical mean-field theory (DMFT) - both involve an impurity-solver that solves an auxiliary system. The difference, however, lies in the following points:
\begin{itemize}
	\item While DMFT primarily works with Greens functions and self-energies, this method involves Hamiltonians. The impurity-solver in DMFT provides an impurity Greens function (which is then equated with the local Greens function of the bath), while the impurity-solver in this method actually provides a low energy Hamiltonian.
	\item The final step of DMFT is the self-consistency equation, where the impurity and bath-local quantities are set equal. This ensures all sites, along with the impurity site, have the same self-energy, something which is required on grounds of  translational invariance. The present method, however, brings about the translational invariance in a different way. It symmetrizes the Hamiltonians itself, such that all quantites then derived from the Hamiltonian are then guaranteed to have the symmetry.
\end{itemize}
The meaning of each of these statements will become clearer when we describe the method in more detail.

@@

With some knowledge of the RG procedure, one can even write down the relation between the Hubbard dimer couplings $t^D, U^D$ and the parent Hubbard model parameters $t^H, U^H$. We have seen previously in another work that in the absence of any explicit spin or charge isospin exchange couplings, the impurity-bath hybridisation coupling $t^A$ does not flow under the RG. In going from the Hubbard model to the auxiliary model, we replace the non-local operator $c_i$ with the local operator $c_d$. If we define the normalization of the Fourier transform such that both spaces have $\frac{1}{\sqrt N}$, then the auxiliary model coupling can be written as $t^A = \sqrt N t^H$. When we write the fixed-point hopping purely in terms of zero mode, another such factor appears: $\sum_k c_k = \sqrt N c_0$, such that $t^D = \sqrt N (t^A)*$. Combining these, we get
\[ t^D = \sqrt N \times (t^A)^* = \sqrt N \times t^A = N \times t^H \]
As for the on-site repulsion $U^H$, we will constrain the RG flows such that the fixed-point value of the impurity ons-te repulsion $U^A$ is identical to that of the on-site repulsion of the bath, $U_b$. A sensible choice for the bath on-site repulsion is simply $U^H\times N$. The factor of $N$ maintains the extensivity of the bath correlation term. We can therefore write
\[U^D \equiv (U^A)* = U_b = N \times U^H\]

@@

\item Obtain the metal insulator transition of the 2D Hubbard model on the square lattice from our formalism. Compare with what is obtained from DMFT and its improvements. Also, determine the nature of the bath $\Sigma (k,\omega)$ for the transition point.
\item While we have provided expressions for the single particle Greens functions of the $N$-site Hubbard model from their equivalent single particle Greens functions of the Hubbard dimer, we expect that eq.\eqref{green_eq_final} holds quite generally for the two-particle Greens function sector as well. We will provide these expressions at a later point in time. 
\item Study various other models of strong correlation with this approach:
		\item Heisenberg model, by starting from a Kondo model effective Hamiltonian
		\item Periodic Anderson model, by starting from a SIAM with a dispersive bath
		\item Periodic Kondo model, by starting from a Kondo model with a dispersive bath
		\item Hubbard-Heisenberg model, by starting from a generalized Anderson molecule (Anderson molecule with two-particle spin and charge interactions between the two sites)
